\documentclass{article}

\begin{document}
% Research into:
% - Eigenfaces
% - Sparse Low Rank Bilinear Discriminative Model
% - What are liveness tests
% - How can we test a system that we create?
% - What test data is available? ROSE-Youtu Face liveness detection dataset
% - Deep Learning based face liveness detection in videos
% - Cameras used: mobile cameras (most methods use average resolution images from webcams or camera phone)
% - "Deep learning based face liveness detection in videos" https://ieeexplore.ieee.org/document/8090202/
% - Ideas: texture based - an image of a face will have the facial textures, while the texture of a piece of paper is very different.
% - Video vs Photo. Wtih a video, you don't just use the subject image, but also factor in movement and changes.
    
    \paragraph{Title}
        Facial Authentication System for the Web
    \paragraph{Project Type}
        Computer Vision, Image Processing and Security
    \paragraph{Description}
        - Traditional username and password focused approaches to authentication have drawbacks (such as password leaks)
        - Existing biometric methods have their problems when applied to a web system, due to the transparency of web systems.
        - Overcoming the transparency hurdle would produce a secure method of authentication for the web, using faces of users.
        - Using multiple methods of facial recognition, facial liveness tests, coupled with implementation details, these can be used to create a robust
        authentication service.
    \paragraph{Preliminary Preparation}
        \begin{itemize}
            \item Existing biometric web-based authentication methods, how do they work, what are their benefits/drawbacks?
            \item What spoofing methods could be undertaken, and how can we prevent these?
            \item What are the privacy concerns regarding a facial recognition approach, and how can these be mitigated?
            \item How can this be integrated into a web service?
            \item Use as a single sign on service (SSO). What protocols are there, how do they work, how can we integrate our system into these standards?
        \end{itemize}
    \paragraph{Minimum Objectives}
        \begin{itemize}
            \item Server that recognises a user given their face (therefore carrying out authentication), generating a token for a user given their face. This token can be used for authorization.
            \item 
        \end{itemize}
    \paragraph{Intermediate Objectives}
        \begin{itemize}
            \item Liveness tests - how can we ensure the user input image is of a person, and not a printout of someone's face?
            \item Scalable system - providing a service layer which is usable by many other users for a variety of uses, and that can scale up if required.
        \end{itemize}
    \paragraph{Advanced Objectives}
        \begin{itemize}
            \item Preventing replay attacks - preventing someone from intercepting someone's facial image, and using it to gain access.
        \end{itemize}
    \paragraph{References}
        \begin{itemize}
            \item Keras (https://keras.io) for Machine Learning
            \item OpenCV (https://opencv.org/) for image Processing
            \item 
        \end{itemize}

    \paragraph{Time Management - Project Plan}
    
    Throughout the project, an agile method shall be conducted. Each sprint shall last two weeks
    starting on the Friday (after a supervisor meeting), 
    with a mid-sprint meeting the following Friday. Start/end sprint meetings shall consist of what existing work has been done, along with what is needed to be focused on in the following sprint. The mid-sprint meetings
    are there to spot problems throughout the sprint cycle, to advise on a different approach or just for general troubleshooting. Trello shall be used to keep an Agile board of tasks that are "To Do", "In Progress",
    or "Done". 

    \textbf{INSERT GANTT CHART HERE SHOWING TASKS/SPRINTS}
    
\end{document}