\documentclass[10pt,a4paper]{article}
\usepackage{times}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{durhampaper}
\usepackage{subfigure}
% \usepackage{harvard}
% \usepackage[moderate]{savetrees}
\usepackage{url}

\title{Facial Liveness Testing: For The Web}
\author{} % leave; your name goes into \student{}
\student{Ryan Collins}
\supervisor{Prof A. Krokhin}
\degree{MEng Computer Science}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
% These instructions give you guidelines for preparing the final paper.  DO NOT change any settings, such as margins and font sizes.  Just use this as a template and modify the contents into your final paper.  Do not cite references in the abstract.

% The abstract must be a Structured Abstract with the headings {\bf Context/Background}, {\bf Aims}, {\bf Method}, {\bf Results}, and {\bf Conclusions}.  This section should not be longer than half of a page, and having no more than one or two sentences under each heading is advised.
\paragraph{Context/Background}
    TODO

\paragraph{Aims}
    TODO

\paragraph{Method}
    TODO

\paragraph{Results}
    TODO
\paragraph{Conclusions}
    TODO

\end{abstract}

\begin{keywords}
Facial liveness, convolutional neural networks, image quality metrics
\end{keywords}

\section{Introduction}
    % What is the project about?
    Currently, username and password authentication is commonplace throughout the web. However, username and password
    based authentication systems have a number of problems. Some common passwords can be broken using dictionary attacks,
    especially if they consist partially or entirely of a word in a standard dictionary. Furthermore, the process of shoulder surfing is possible (watching out
    for someone's password, and how they type it).

    An easy to use system is necessary to remove the choice from the user (in terms of password), relying on the user being automatically
    detected, and several confirmation methods to ensure the user is indeed who they say they are (and not just someone spoofing the system).
    Before such a system is developed, a facial liveness testing method must be found that operated in near real-time, and that is fairly accurate.


\section{Related Work}
    TODO related Work
    % literature review esqe stuff.

\section{Solution}
    % Solution to the problem

    \subsection{A system for preventing 3D spoofing attacks}
        While the systems before might go partially towards preventing 3D spoofing attacks, we now propose a method
        that is designed for classifying facial liveness based on a 3D point cloud.

        \subsubsection{Point Cloud Reconstruction}
            In order to classify an image/video, a 3D point cloud needs to be created, containing many 3D points $(x,y,z)$
            of a user's face. While 3d reconstruction is easier with videos (using structure from motion or other multiview based methods),
            there also exist image-based reconstruction methods such as vrn \textbf{CITE VRN network model here for 3d reconstruction}, which are
            more specific and designed for reconstructing faces based on images.

        \subsubsection{3D point cloud classification}
            Once the 3D reconstruction is obtained, one can then classify this using some model to produce the fake/real metric.

            For points, PointNet is a model that can be used \textbf{EXPLAIN POINTNET}

            However, as we are using voxels, there is a more specialised architecutre called Voxnet that is designed for classifying
            3d volume-based objects. This is the model used here.
\section{Results}
    % based on the solution, what results did we yield? What did we find out?
    TODO results
\section{Evaluation}
    % How well our system works, how well did it assess stuff, and how it can be improved.
    % what are the uses of our research? e.g. influence and improve the design of xyz...
    TODO evaluation


    % Improvements:
    % 3D attacks more difficult. One could extend this method using 3D reconstruction (sfm based on videos)
    % then recovering 3D details, and using these as input features.
    % this would allow for 3D reconstruction to some extent. Would require video input.
\section{Conclusions}
    % overall, what did hte projct show?


\bibliographystyle{dinat}
\bibliography{report}

\end{document}